A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-31 manuscript.Rmd
fix typo

Second, we rely on dynamic document generation.
The traditional way of writing a scientific report based on a statistical data analysis uses two separate steps which are conducted in two different programs.
In a word processor the researcher writes the text and in another software they conduct the analysis.
Both steps are linked by manually copying and pasting results from one software to the other; a process that often produces in inconsistencies [@nuijtenPrevalenceStatisticalReporting2016].

>>>>

Second, we rely on dynamic document generation.
The traditional way of writing a scientific report based on a statistical data analysis uses two separate steps which are conducted in two different programs.
In a word processor the researcher writes the text and in another software they conduct the analysis.
Both steps are linked by manually copying and pasting results from one software to the other; a process that often produces inconsistencies [@nuijtenPrevalenceStatisticalReporting2016].
